\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ganbat Selenge} \\ \vspace{8pt}
    \small (+36) 204998873 $|$ 
    \href{mailto:s.ganbat24@gmail.com}{\underline{s.ganbat24@gmail.com}} $|$ 
    Debrecen, Hungary $|$
    \href{https://www.linkedin.com/in/ganbat24/}{\underline{linkedin.com/in/ganbat24}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Graduate Mechatronics Engineer (GPA: 4.7/5.0) with a focus on robotics, autonomous systems, and cyber-physical control. Experienced in ROS 2, sensor fusion (EKF, LiDAR), and full-stack software development. Proven ability to bridge mechanical design and intelligent software through high-level academic research and industrial internships.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Debrecen}{Debrecen, Hungary}
      {Bachelor of Science in Mechatronics Engineering}{Sep 2022 -- Feb 2026}
      \resumeItemListStart
        \resumeItem{\textbf{Grade: Excellent (4.7/5.0)} | Total Credits: 231 ECTS}
        \resumeItem{\textbf{Specialization:} Mechatronic Systems (Control Theory, Robotics, and Embedded Systems)}
        \resumeItem{\textbf{Honors:} Consistently achieved "Excellent (5)" grades in core technical modules including Robots and Robotics Technology, Applied Automatization, and Cyber-Physical Systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Robotics \& Control}{: ROS 2, Cyber-Physical Systems, PID Control, Kalman Filters (EKF), Applied Automatization} \\
     \textbf{Software \& Tools}{: MATLAB, Simulink, LabVIEW, AutoCAD, NI Multisim, KiCad, Git/GitHub, Gazebo} \\
     \textbf{Languages}{: C/C++, Python, JavaScript (Angular/Angular JS), Rust} \\
     \textbf{Hardware}{: Raspberry Pi 4, Arduino Nano ESP32, 2D LiDAR, IMU, Ultrasonic/IR Sensors}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Research \& Engineering Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Coordination and Control of Mobile Robot Swarms (BSc Thesis)}} {ROS 2, Python, C++}
          \resumeItemListStart
            \resumeItem{Wrote a thesis developing a Leader-Follower cooperative localization framework.}
            \resumeItem{Implemented an Extended Kalman Filter (EKF) to fuse LiDAR perception data with wheel odometry and IMU.}
            \resumeItem{Engineered a perception pipeline using DBSCAN clustering for real-time tracking of follower robots.}
            \resumeItem{Developed and validated the system in both Gazebo simulation and on physical Raspberry Pi 4 hardware.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Autonomous \& Assistive Robotics Research Group (A²R)}{Debrecen, Hungary}
      {Undergraduate Researcher}{Feb 2025 -- Feb 2026}
      \resumeItemListStart
        \resumeItem{Conducted research focusing on multi-robot coordination and autonomous navigation.}
        \resumeItem{\textbf{Thesis:} Developed a Leader-Follower cooperative localization framework using ROS 2, Python, and C++.}
      \resumeItemListEnd

    \resumeSubheading
      {Lime Light TechLead}{Oslo, Norway}
      {Intern - Renewable Energy Management}{Jul 2024 -- Sep 2024}
      \resumeItemListStart
        \resumeItem{Engineered and monitored solar panel systems, ensuring optimal operation and power output.}
        \resumeItem{Diagnosed hardware faults in systems and performed preventative maintenance on monitoring equipment.}
      \resumeItemListEnd
      
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{Grapecity Mongolia} & {Ulaanbaatar, Mongolia} \\
      \textit{\small Frontend Developer (Contract)} & \textit{\small Jan 2021 -- Feb 2021} \\
      \textit{\small Frontend Developer (Contract)} & \textit{\small May 2020 -- Aug 2020} \\
    \end{tabular*}\vspace{-7pt}
    \resumeItemListStart
        \resumeItem{Architected a banking application using Angular JS, implementing secure account management and transaction tracking.}
        \resumeItem{Developed the UI for the "UB Parking" system, focusing on responsive design and real-time data visualization.}
        \resumeItem{Collaborated with backend teams to debug API integrations and optimize application load times.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English (C1 Proficient)}, \textbf{Mongolian (Native)}
    }}
  \end{itemize}

\end{document}